---
title: "Nonparametric Boostraping"
output: 
  html_notebook:
    theme: cosmo
    highlight: monochrome
    toc: true
    toc_float: true
    toc_depth: 4
    number_sections: true
    code_folding: show
    df_print: kable
  github_document: default
---
<style>

h1.title { 
  font-size: 18pt; 
  color: DarkBlue; 
} 

body, h1, h2, h3, h4 {
    font-family: "Palatino", serif;
}

body {
    font-size: 12pt;
}

/* Headers */
h1,h2,h3,h4,h5,h6{
  font-size: 14pt;
  color: #00008B;
}

body {
    color: #333333;
}
a, a:hover {
    color: #8B3A62;
}
pre {
    font-size: 12px;
}
</style>



# Preliminarities 

This notebook is based on the following article

- Quick-R: Bootstrapping. (2018). Statmethods.net. Retrieved 7 May 2018, from <https://www.statmethods.net/advstats/bootstrapping.html>

List of packages

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(boot)
```


# Bootstrapping a Single Statistic (k=1)

The following example generates the bootstrapped 95% confidence interval for R-squared in the linear regression of miles per gallon (`mpg`) on car `weight` (wt) and displacement (`disp`). The data source is mtcars. The bootstrapped confidence interval is based on 1000 replications.

First, let us definie a function to obtain R-Squared from the data  

```{r}
rsq <- function(formula, data, indices) {
  d <- data[indices,] # allows boot to select sample 
  fit <- lm(formula, data=d)
  return(summary(fit)$r.square)
} 
```




# Bootstrapping several Statistics (k>1)